\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{xypic}
\usepackage{txfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amscd}
\usepackage{amsmath, mathtools,amssymb}
\usepackage{amsfonts,semantic,colortbl,mathrsfs,stmaryrd}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{graphicx}
\date{Feb 14, 2012}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{fact}[thm]{Fact}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{eg}{Example}
\newtheorem{hw}{Problem}
\newcommand{\xor}{\otimes}
\newenvironment{sol}
  {\par\vspace{3mm}\noindent{\it Solution}.}
  {\qed}
\begin{document}
\begin{center}
{\LARGE\bf Homework 7}\\
\vspace{2mm}
\end{center}

\begin{hw}
\begin{enumerate}
  \item Prove that, for every integer $n$, there exists a coloring of the edges of the complete graph $K_n$ by two colors so that the total number of monochromatic copies of $K_4$ is at most ${n\choose 4}2^{-5}$.
  \item Give a randomized algorithm for finding a coloring with at most ${n \choose 4}2^{-5}$ monochromatic (i.e. single-color) copies of $K_4$ that runs in expected time polynomial in $n$.
\end{enumerate}
\end{hw}

\begin{sol}
\renewcommand{\qedsymbol}{}
\begin{itemize}
\item [(a)] $X$ is the random variable denoting the number of monochromatics copies of $K_4$. The probability that a certain $4-subset$ forms a monochromatic $K_4$ is $2\times 2^{-6}$, where 2 is for the two different colours. Then, $$E[X]=
{n\choose 4} \times 2\times 2^ { -6} = {n\choose 4}2^{-5}$$
\item [(b)] ) Colour edges independently and uniformly. Let $p = Pr(X\leq {n\choose 4}2^{-5})$. Then we have
$${n\choose 4}2^{-5} = E[X] = \sum_{i \leq {n\choose 4}2^{-5}}{iPr(X=i)} + \sum_{i \geq {n\choose 4}2^{-5}}{iPr(X=i)} \geq p + (1-p)({n\choose 4}2^{-5}+1)$$ which implies that $$\frac{1}{p} \leq {n\choose 4}2^{-5}$$
Thus, the expected number of samples is at most ${n\choose 4}2^{-5}$. Testing this to see if $X \leq {n\choose 4}2^{-5}$ can be done in $O(n^4)$ time. As such the algorithm can be done in polynomial time.
\end{itemize}
\end{sol}


\begin{hw}
Use the Lovasz local lemma to show that if \[4 {k \choose 2} {n \choose {k-2}}2^{1-{k\choose 2}}\leq 1\]
then it is possible to color the edges of $K_n$ with two colors so that it has no monochromatic(i.e. single color) $K_k$ subgraph.
\end{hw}

\begin{sol}
\renewcommand{\qedsymbol}{}
Consider a random 2-coloring of the graph.
Let $E_i$ be the case that the ith $k-set$ is a monochromatic clique.

$$Pr(E_i)=2\cdot (\frac{1}{2})^{k\choose 2}=2^{1-{k\choose 2}}$$
Then we have the number of $k-clique$ is bounded by ${k \choose 2} {n \choose {k-2}}$.
Thus, whenever 
$$4 {k \choose 2} {n \choose {k-2}}2^{1-{k\choose 2}}\leq 1$$
we can apply the general Lovasz local lemma and show that there exists a coloring satisfys the problem requirement.

\end{sol}

\end{document}

%%% Local Variables:
%%% mode: tex-pdf
%%% TeX-master: t
%%% End: